ohun_paper_analyses

### 2022-07-13 README.Rmd
Update README.Rmd

---
title: ohun_paper_analyses
author: AUTOR NAME
output: github_document
date: `r format(Sys.Date(), "%d-%m-%Y")`
editor_options:
  chunk_output_type: console
---

<!-- Short Description  -->
This is a short description of the project

@@

## Table of contents
* [General info](#general-info)
  * [Analyses](#Analyses)
    * [To do list](#to-do-list)
      * [Contact](#contact)

@@

General information about the project (study system, goals, etc)

## Analysis

* Analysis 1

@@

*  Something not finished yet

@@

* Do the next analysis

@@

## Contact
Created by [Autor name](website_URL)

>>>>

---
title: ohun_paper_analyses
author: Marcelo Araya Salas
output: github_document
date: `r format(Sys.Date(), "%d-%m-%Y")`
editor_options:
  chunk_output_type: console
---

<!-- Short Description  -->
Data analysis and manuscript writting for method paper on the R package ohun

@@

## Table of contents
* [General info](#general-info)
    * [To do list](#to-do-list)
      * [Contact](#contact)

@@

Data analysis and manuscript writting for method paper on the R package ohun

@@

*  Writting

@@

* Add citations

@@

## Contact
Created by [Marcelo Araya-Salas](marceloarayasalas.weebly.com/)
